Assessing primitives performance\\ on multi-stage execution

### 2018-05-17 paper.tex
update bench table + llvm results

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0,
	]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.3841129   0.001065645
3   0.2692461   0.0006797441
4   2.477776   0.009248639
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.7062775   0.001896893
3   0.4939137   0.0013709049
4   3.744060   0.012604598
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   1.7187980   0.005024289
3   1.1879773   0.0033351563
4   7.245105   0.046617323
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}
 \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   12.6151983   0.080605928
3   7.5970353   0.0396763134
4   18.935631  0.124523834
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   25.7537381   0.169939301
3   11.6939697   0.0497562584
4   27.829197  0.142897191
};
      \end{axis}
    \end{tikzpicture}

   \end{subfigure}
   \subcaption*{\textbf{LLVM-Mac}\vspace{-0.2cm}} %change vspace based on fig position
    \end{subfigure}
   \caption{String comparison benchmarks for strings of different sizes on different architectures.}
   \label{fig:bench}
\end{figure*}
\begin{table*}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
    & & 0 & 1 & 5 & 100 & 1000 \\
   \hline
  \multirow{2}{*}{SlangPlugin} &GCC& 0.3375 +- 0.0016 & 0.5654 +- 0.0078 & 1.3150 +- 0.0205 & 8.9585 +- 0.1170  & 14.7789 +- 0.1471 \\
  							   &LLVM& 0.3036 +- 0.0018 & 0.5567 +- 0.0010 & 1.2296 +- 0.0018 & 6.6033 +- 0.0248  & 9.2138 +- 0.0140 \\
   \hline
  \multirow{2}{*}{PureSlang} &GCC& 1.0778 +- 0.0054 & 1.8169 +- 0.0191 & 3.8190 +- 0.0545 & 15.8095 +- 0.3005 & 24.4178 +- 0.1863\\
 							 &LLVM& 0.8545 +- 0.0061 & 1.5605 +- 0.0064 & 2.8205 +- 0.0080 & 10.3029 +- 0.0615  & 13.4385 +- 0.0402 \\
   \hline
  \multirow{2}{*}{Slang+JIT} &GCC& 2.4904 +- 0.0043 & 3.5378 +- 0.0124  & 6.7405 +- 0.0108 & 16.7527 +- 0.1063 & 24.4801 +- 0.0950\\
 							&LLVM & 2.2507 +- 0.0413 & 3.7545 +- 0.0111 & 7.0898 +- 0.0140 & 17.9796 +- 0.1013  & 26.4048 +- 0.0930 \\
  \hline
\end{tabular} 
\vspace{0.2cm}
\caption{Benchmark results with standard errors. Average relative speed-up regarding baseline.}
\label{tab:detail_bench}
\end{table*}

>>>>

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0,
	]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.3856066   0.0003752957
3   0.2087539   0.0002019377
4   2.571790   0.003453254
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.6684630   0.0010425882
3   0.3648824   0.0006104112
4   3.591927   0.007633769
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   1.6386585   0.0100987883
3   0.8953226   0.0055539752
4   6.956865   0.041610797
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}
 \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   11.6376234   0.0575507774
3   6.1978094   0.0180202851
4   17.274749  0.107117757
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   23.9578625   0.1389707435
3   10.6698346   0.0065863712
4   25.399095  0.181054897
};
      \end{axis}
    \end{tikzpicture}

   \end{subfigure}
   \subcaption*{\textbf{LLVM-Mac}\vspace{-0.2cm}} %change vspace based on fig position
    \end{subfigure}
   \caption{String comparison benchmarks for strings of different sizes on different architectures.}
   \label{fig:bench}
\end{figure*}
\begin{table*}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
    & & 0 & 1 & 5 & 100 & 1000 \\
   \hline
  \multirow{2}{*}{SlangPlugin} &GCC& 0.4222 +- 0.0008 & 0.7674 +- 0.0011 & 1.8906 +- 0.0119 & 13.1218 +- 0.0171  & 25.3595 +- 0.1742 \\
  							   &LLVM& 0.3856 +- 0.0004 & 0.6685 +- 0.0010 & 1.6387 +- 0.0101 & 11.6376 +- 0.0576  & 23.9579 +- 0.1390 \\
   \hline
  \multirow{2}{*}{PureSlang} &GCC& 1.0288 +- 0.0046 & 1.8431 +- 0.0116 & 4.0412 +- 0.0611 & 17.7084 +- 0.1059 & 25.4258 +- 0.1621\\
 							 &LLVM& 0.2088 +- 0.0002 & 0.3649 +- 0.0064 & 0.0006 +- 0.0056 & 6.1978 +- 0.0180  & 10.6698 +- 0.0066 \\
   \hline
  \multirow{2}{*}{Slang+JIT} &GCC& 2.4290 +- 0.0029 & 3.5170 +- 0.0197  & 7.1216 +- 0.0105 & 18.5537 +- 0.0238 & 26.7626 +- 0.1861\\
 							&LLVM & 2.5718 +- 0.0035 & 3.5919 +- 0.0076 & 6.9569 +- 0.0416 & 17.2747 +- 0.1071  & 25.3991 +- 0.1811 \\
  \hline
\end{tabular} 
\vspace{0.2cm}
\caption{Benchmark results with standard errors. Average relative speed-up regarding baseline.}
\label{tab:detail_bench}
\end{table*}
